SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-19 Chapters/sdm-autocorrelation.tex
SDM Autocorrelation theorems.

@@

From Lemma \ref{thm:sdm-access-radius}, we know that $r = n/2$ for $n$ sufficiently large.

@@

In Figure \ref{fig:sdm-10kbits-figure-7-3}, $n=10,000$ and we can notice that the autocorrelation has vanished as predicted by Theorem \ref{thm:sdm-autocorrelation-convergence}.

@@

  \caption{Given an address $x$ and a dimension $i$, how many hard locations with bitmatches in $i$ are activated by reading at $x$?  The histogram was obtained through numerical simulation. The red curve is the theoretical normal distribution found in Theorem \ref{T2}.}
  \label{fig:sdm-10kbits-figure-7-3}
\end{figure}

>>>>

\begin{lemma}
Let $\Phi(x)$ be the cdf of the standard normal distribution. Then, $n \rightarrow \infty \Rightarrow P(x_i = y_i | d(x, y) \le r) = \frac{1}{2} \frac{\Phi(z_1)}{\Phi(z_2)}$, where $z_1 = \frac{2r - n + 1}{\sqrt{n-1}}$ and $z_2 = \frac{2r - n}{\sqrt{n}}$.
\label{thm:sdm-T1-n-large}
\end{lemma}
\begin{proof}

From the approximation of the Binomial distribution $B(a, 0.5)$ by the Normal distribution $\mathcal{N}(\mu = a/2, \sigma^2 = a/4)$, we conclude that, for $a$ sufficiently large, the cdf of the Binomial is approximately equal to the cdf of the Normal distribution. Thus,

$$
\frac{1}{2^a} \sum_{k=0}^{b} \binom{a}{k} = \Phi \left( \frac{b-a/2}{\sqrt{a}/2} \right) = \Phi \left( \frac{2b-a}{\sqrt{a}} \right)$
$$

Thus,

$$
\sum_{k=0}^{b} \binom{a}{k} = 2^a \Phi \left( \frac{2b-a}{\sqrt{a}} \right)$
$$

The result comes directly from applyting the equation above in $P(x_i = y_i | d(x, y) \le r)$.

@@

From Lemma \ref{thm:sdm-access-radius}, we know that $r = n/2$ for $n$ sufficiently large. Thus, replacing $r = n/2$ in Lemma \ref{thm:sdm-T1-n-large}, $P(x_i = y_i | d(x, y) \le r) = \frac{\Phi(z_1)}{2 \Phi(z_2)}$, where $z_1 = \frac{1}{\sqrt{n-1}}$ and $z_2 = 0$.

As $n \rightarrow \infty$, $z_1 \rightarrow 0$, and $P(x_i = y_i | d(x, y) \le r) = \frac{\Phi(0)}{2 \Phi(0)} = 1/2$. \qed

Another way to proof is to divide into two cases:

@@

In Figure \ref{fig:sdm-10kbits-figure-7-3}, with $n=10,000$ and $r=4,845$, we can notice that the autocorrelation has vanished as predicted by Theorem \ref{thm:sdm-autocorrelation-convergence}. In fact, in this case, $P(x_i = y_i | d(x, y) \le r) = 0.5039895557907589$.

@@

  \caption{The same setup as in Figure \ref{fig:sdm-10000w-table-7-2}, but for $n=10,000$. It shows that the interference has gone away when $n$ is sufficiently large.}
  \label{fig:sdm-10kbits-figure-7-3}
\end{figure}
